The Anatomy of a Temporal Summarization System

### 2015-01-25 algorithm/ap.tex
Read and commented on algorithm sections

To address the uncertain in salience predictions, we adopted an algorithm known as affinity propagation (AP) \cite{dueck2007non}.  AP is a message passing algorithm that identifies both exemplar data points and assignments of each point to an exemplar.  This is done iteratively by passing \emph{responsibility} and \emph{availability} messages between data points that quantify the fitness of one data point to represent another, and the fitness of a data point to be represented based on the choices of other data points respectively.

@@

% \subsubsubsection{Semantic Similarity}
% \label{subsec:semsim}
The AP algorithm requires two data structures: the semantic similarity matrix $\candidateSimMat$ and the preference vector $\preferences$.  In order to construct $\candidateSimMat$, we use the weighted textual matrix factorization (WTMF) model of \cite{guo2012simple}. This  model can be thought of as a variant of latent semantic analysis \cite{deerwester:lsa},  where strings, sentences in our case, are projected into a lower dimensional space.  We then use the cosine similarity of embedded vectors in this space to define entries in $\candidateSimMat$.  The preference vector $\preferences$ is constructed by using salience scores rescaled to lie within the  range $(-3, -2)$.  \fdcomment{not sure how much we have to justify this.}

>>>>

To address the uncertainty in salience predictions, we adopted an algorithm known as affinity propagation (AP) \cite{dueck2007non}.  AP is a message passing algorithm that identifies both exemplar data points and assignments of each point to an exemplar.  This is done iteratively by passing \emph{responsibility} and \emph{availability} messages between data points that quantify the fitness of one data point to represent another, and the fitness of a data point to be represented based on the choices of other data points respectively.

@@

% \subsubsubsection{Semantic Similarity}
% \label{subsec:semsim}
The AP algorithm requires two data structures: the semantic similarity matrix
$\candidateSimMat$ and the preference vector $\preferences$.  In order to
construct $\candidateSimMat$, we use the weighted textual matrix factorization
(WTMF) model of \cite{guo2012simple}. This  model can be thought of as a
variant of latent semantic analysis \cite{deerwester:lsa},  where strings,
sentences in our case, are projected into a lower dimensional space.  We then
use the cosine similarity of embedded vectors in this space to define entries
in $\candidateSimMat$.
%KM - Include advantage. Tried below
This approach allows us to measure semantic similarity as opposed to simple
word overlap.
The preference vector $\preferences$ is constructed by using salience scores rescaled to lie within the  range $(-3, -2)$.  \fdcomment{not sure how much we have to justify this.}

### 2015-01-25 algorithm/novelty.tex
Read and commented on algorithm sections

\subsubsection{Ensuring Novelty with Respect to Previous Updates}
\label{sec:novelty}
After we run AP clustering, we have a set of candidates for the current hour.  In order to avoid outputting redundant updates, we computed the semantic similarity between the exemplar sentences and previously output sentences.  We then removed those sentences which were above some similarity threshold.  We selected the threshold by inspecting the distribution of similarities between sentences associated with the same sub-event in the training set and the distribution of similarities between random pairs of sentences.

>>>>

\subsubsection{Ensuring Novelty with Respect to Previous Updates}
\label{sec:novelty}
After we run AP clustering, we have a set of candidates for the current hour.  In order to avoid
%KM - word change
%outputting
producing
redundant updates, we computed the semantic similarity,
%KM - You could give the semantic similarity algorithm a name. THat woudl make it easier to refer to. In any case, you need to specify the method you use here. I added clause below. Coudl remove it if you name the algorithm.
using the same method as used in salience prediction,
between the exemplar sentences and previously output sentences.  We then removed those sentences which were above some similarity threshold.  We selected the threshold by inspecting the distribution of similarities between sentences associated with the same sub-event in the training set and the distribution of similarities between random pairs of sentences.
